Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. by
In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for
stable application activity data that can be used as a baseline
or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, namely the latency data of all recorded traces
by the tracing system, and operating data that occurs on the critical path of all traces along with
its latency value which will be stored as a key-value pair as well.

>>>>

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.

The next phase is the periodic analysis phase. This phase will run continously and the analysis will be run periodically at intervals of 5 minutes
very. This is done to continuously detect whether there is a regression and
immediately determine the source of the regression if it occurs. There are several stages of analysis
to be carried out in this phase. The first analysis stage will compare the results
transformation of data latency of all ongoing traces periodically
with the baseline latency artifact from the loading phase. The comparison will be made within a certain period. The comparison of the two latency data will produce
Kolmogorov-Smirnov statistics. If Kolmogorov-Smirnov statistics are generated
indicates that the two samples of latency data come from two different distributions
different, then it can be an indication that there has been a regression in the data capture period
the traces.
